Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-04 RR_manuscript/Draft_RR.Rmd
include paragraph on funnel plots in section 2.4.2

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

@@

# Methods (mostly copy-paste from Evo-RR)

@@

>>>>

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(patchwork)
```

@@

# Methods

@@

Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
This will be achieved through inspection of funnel plots [@light1984; for a review see @egger1997; and @sterne2005; for a critique @lau2006].
In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the *x*-axis and estimated error (i.e. standard deviation) on *y*-axis.
In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \@ref(fig:funnel-plot)).
A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.

```{r funnel-plot, include=TRUE, fig.cap="Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes. The vertical dashed line represents the meta-analitical mean.", fig.dim = c(6, 2)}
meta_est <- 0

datasets <- map(
  c(0, 0.1, -0.1),
  function(.x) {
    set.seed(101)
    sd <- runif(100, min = 1, max = 10)
    est <- rnorm(length(sd), mean = meta_est, sd = 0.1*sd) + .x * sd
    tibble(est, sd)
  }
)

plots <- map(
  datasets,
  function(.x) {
    ggplot(.x, aes(est, sd)) +
      geom_vline(aes(xintercept = meta_est), linetype = "dashed") +
      geom_point(colour = "black", size = 1, alpha = 0.5) +
      scale_y_reverse() +
      labs(est = element_blank(), sd = element_blank())  +
      xlim(-3, 3) +
      theme_minimal()
  }
)

plots[[1]] + labs(title = "(a) no bias") +
  plots[[2]] + labs(title = "(b) positive bias") +
  plots[[3]] + labs(title = "(c) negative bias")
```

```{r funnel-calc, include=FALSE, eval=FALSE}
# meta_bm is the meta-analytical Bayesian regression model
meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"
meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]

# estimated_tbl contains the standardized effect sizes
se_range <- seq(0, max(estimated_tbl$Est.Error), by = 0.001)

ci <- tibble(
  x_seq = se_range,
  ci_lo = meta_ln_bm_est - 1.96 * se_range,
  ci_up = meta_ln_bm_est + 1.96 * se_range
)

estimated_tbl %>%
  ggplot(aes(Estimate, Est.Error)) +
  geom_line(aes(y = x_seq, x = ci_up), data = ci) +
  geom_line(aes(y = x_seq, x = ci_lo), data = ci) +
  geom_vline(aes(xintercept = 0), colour = "grey") +
  geom_vline(aes(xintercept = meta_ln_bm_est)) +
  annotate(
    "rect",
    ymin = -Inf, ymax = Inf,
    xmin = meta_bm_q2.5, xmax = meta_bm_q97.5,
    alpha = 0.5, fill = "#a6cee3") +
  geom_point(size = 3) +
  scale_y_reverse()
```
